Fast Sorting on Modern Computers

### 2005-08-18 docs/tech_report/conclusions.tex
fixed up the heap stuff in the conclusion

In heapsort, we found a pattern of branch mispredictions when using a fanout in
our 8-heap, and that this pattern matched closely that of selection sort,
discussed above. Despite this property, the number of mispredictions using an
8-heap was greater than when using a 4-heap.

>>>>

In heapsort, we found a pattern of branch mispredictions when using a fanout in
our 8-heap, and that this pattern matched closely that of selection sort,
discussed above. We found that the approximated results using $H_N$ was similar to
our expected results for large arrays, and followed a similar pattern for small
arrays.

Also in heapsort, the number of mispredictions decreases depending on how much
the heap fans out.  Despite this property, the number of mispredictions using an
8-heap was greater than when using a 4-heap, due to the increased total number
of branches.
